---
title: "Expanding your graphical repertoire"
date: "2022-02-21"
output:
  xaringan::moon_reader:
    css: ["default", "middlebury", "middlebury-fonts", "custom.css"]
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: 16:9
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

library("data.table")
library("ggplot2")
library("knitr")
library("kableExtra")
library("graphclassmate")
library("wrapr")
library("gapminder")

my_table <- function(x){
 x %>% 
  kbl(col.names = NULL) %>%
  kable_styling(position = "float_left", font_size = 18) %>%
  column_spec(1, background = "white") %>%
  column_spec(2, background = "white")  %>%
  add_header_above(c("Data structure" = ncol(x)))
}
```

class: right

.left-column[
data


design
]

.right-column[

# Expanding your graphical repertoire

## Matching chart type to data structure


<br>

<br>

Richard Layton   

2022-02-14

<br>

<br>

<https://graphdr.github.io/data-stories/>

<https://github.com/graphdr>

<a href="mailto:graphdoctor@gmail.com">graphdoctor@gmail.com</a>
]












---
class: left

# Our goal is to match chart type to data structure

A list of designs and their permutations for commonly-encountered data structures. 

.pull-left[
**strip chart**

**box and whisker chart** 

**dot chart** &mdash; *faceted, superposed*

**scatterplot**  &mdash; *faceted, superposed*

**time series**  &mdash; *faceted, superposed*

**cyclic time series**  &mdash; *superposed*
]

.pull-right[
**diverging stacked-bar chart**

**scatterplot matrix** 

**conditioning chart** 
]






---
class: left

# Strip chart

Designed to display the distribution of a single quantitative variable.

<div class="my-footer">
<span>Data source: Source  
<a href="https://site">Link</a></span>
</div> 











---
class: left

# Box and whisker chart

Designed to display a 5-point statistical summary of the distribution of a single quantitative variable.

<div class="my-footer">
<span>Data source: Source  
<a href="https://site">Link</a></span>
</div> 














---
class: left

# Dot chart

```{r echo=FALSE}
# initial data carpentry
data(infant_mortality, package = "graphclassmate")
dt <- data.table(infant_mortality)

# recoding
dt[region == "CENS-R1", region := "Northeast"]
dt[region == "CENS-R2", region := "Midwest"]
dt[region == "CENS-R3", region := "South"]
dt[region == "CENS-R4", region := "West"]
dt[race != "Black", race := "Non-Black"]
dt[, county_id := NULL]
dt[age == "15", age := NA]
dt[age == "45-49", age := NA]
dt <- na.omit(dt)
```

```{r echo=FALSE}
# first plot, aggregate by age group
fig1 <- dt[, .(deaths = sum(deaths), births  = sum(births)), by = age]
fig1[, per_thou := 1000 * deaths / births]
```

One quantity that depends on one categorical variable. 

.pull-left[
```{r echo=FALSE, fig.width=7, fig.asp=1/1.7}
ggplot(fig1, aes(x = per_thou, y = age)) +
  geom_point(size = 5, shape = 16, color = rcb("dark_BG")) + 
  theme_graphclass(font_size = 18) +
  labs(x = "US infant deaths per 1000 births, 2007-2016", 
       y = "Age", 
       title = "All US regions") +
  scale_x_continuous(limits = c(3, 18), breaks = seq(0, 50, 5)) +
  theme(axis.title.y = element_text(angle = 0, hjust = 1, vjust = 1))
```
]
.pull-right[

<br>

```{r echo=FALSE}
x <- build_frame(
   "variable"         , "structure" |
   "infant mortality" , "quantitative variable" |
   "mother's age"     , "categorical, ordinal, 6 levels")
my_table(x)
```

<br>

<br>

<br>

A good substitute for many pie charts and bar charts. 
]

<div class="my-footer">
<span>Data source: US Centers for Disease Control and Prevention  
<a href="https://wonder.cdc.gov/lbd-current.html">CDC WONDER Linked Birth / Infant Death Records</a></span>
</div> 












---
class: left

# Dot chart, faceted

One quantity that depends on two independent categorical variables (also called a multiway chart). 

```{r echo=FALSE}
# second plot, age, region
# manually assign factor levels to match the third graph
fig2 <- dt[, .(deaths = sum(deaths), births  = sum(births)), 
           by = c("age", "region")]
fig2[, per_thou := 1000 * deaths / births]
fig2[, region := factor(region, levels = c("West", "Northeast", "South", "Midwest"))]
```

```{r echo=FALSE, fig.asp=0.27, fig.width=16}
ggplot(fig2, aes(x = per_thou, y = age)) +
  facet_wrap(vars(region), ncol = 4) +
  geom_point(size = 5, shape = 16, color = rcb("dark_BG")) + 
  theme_graphclass(font_size = 20) +
  labs(x = "US infant deaths per 1000 births, 2007-2016 (Source: CDC)", 
       y = "Age") + 
  scale_x_continuous(limits = c(3, 18), breaks = seq(0, 50, 5)) +
  theme(axis.title.y = element_text(angle = 0, hjust = 1, vjust = 1))
```
.left-column[
A good substitute for many pie charts and bar charts. 
]
.right-column[
```{r echo=FALSE}
x <- build_frame(
   "variable"         , "structure" |
   "infant mortality" , "quantitative variable" |
   "mother's age"     , "categorical variable, ordinal, 6 levels" |
   "US region"        , "categorical variable, nominal, 4 levels" )
my_table(x)
```
]

<div class="my-footer">
<span>Data source: US Centers for Disease Control and Prevention  
<a href="https://wonder.cdc.gov/lbd-current.html">CDC WONDER Linked Birth / Infant Death Records</a></span>
</div> 










---
class: left

# Dot chart, faceted, superposed

Conditioning multiway data by another independent categorical variable.

```{r echo=FALSE}
# third plot, age, region, race
fig3 <- dt[, .(deaths = sum(deaths), births  = sum(births)), 
           by = c("age", "region", "race")]
fig3[, per_thou := 1000 * deaths / births]

# label data in one panel only
age      <- c("15-19")
region   <- c("West", "West")
race     <- c("Non-Black", "Black")
per_thou <- c(8, 10.5)
my_text  <- data.table(age, region, race, per_thou)
```

```{r echo=FALSE, fig.asp=0.27, fig.width=16}
ggplot(fig3, aes(x = per_thou, y = age, color = race, fill = race)) +
  facet_wrap(vars(reorder(region, per_thou, median)), ncol = 4) +
  geom_point(size = 5, shape = 21) + 
  theme_graphclass(font_size = 20) +
  labs(x = "US infant deaths per 1000 births, 2007-2016 (Source: CDC)", 
       y = "Age") + 
  scale_x_continuous(limits = c(3, 18), breaks = seq(0, 50, 5)) +
  theme(axis.title.y = element_text(angle = 0, hjust = 1, vjust = 1), 
        legend.position = "none") +
  scale_color_manual(values = c(rcb("dark_BG"), rcb("dark_BG"))) +
  scale_fill_manual(values = c(rcb("dark_BG"), "white")) +   
  geom_text(data = my_text, 
            mapping = aes(x = per_thou, y = 5.55, label = race),
            hjust = c(1, 0), 
            size = 6, 
            color = "black")
```
.left-column[
A good substitute for many pie charts and bar charts. 
]
.right-column[
```{r echo=FALSE}
x <- build_frame(
   "variable"         , "structure" |
   "infant mortality" , "quantitative variable" |
   "mother's age"     , "categorical variable, ordinal, 6 levels" |
   "US region"        , "categorical variable, nominal, 4 levels"  |
   "mother's race"    , "categorical variable, nominal, 2 levels")
my_table(x)
```
]

<div class="my-footer">
<span>Data source: US Centers for Disease Control and Prevention  
<a href="https://wonder.cdc.gov/lbd-current.html">CDC WONDER Linked Birth / Infant Death Records</a></span>
</div> 











---
class: left

# Scatterplot

Designed to reveal correlations between two quantitative variables.

```{r echo=FALSE}
# gapminder: world regions
regions <- fread("data/world-regions.csv", header =  TRUE)
regions <- regions[, 
           .(name, four_regions, six_regions, eight_regions)]
setnames(regions, "name", "country")

# gapminder: life expectancy data
life_exp <- fread("data/life_expectancy_years.csv", header =  TRUE)
life_exp <- life_exp[, c("country", "1971":"2021")] 
life_exp <- melt(life_exp,
            id.vars       = "country",
            variable.name = "year",
            value.name    = "lifeExp")
life_exp[, year := as.character(year)]
life_exp[, year := as.integer(year)]

# gapminder: GDP in constant 2011 PPP dollars
gdp <- fread("data/gdp_percapita_ppp.csv", header =  TRUE)
gdp <- gdp[, c("country", "1971":"2021")] 
gdp <- melt(gdp,
            id.vars       = "country",
            variable.name = "year",
            value.name    = "per_capita_gdp")

# convert factors to integers
gdp[, year := as.character(year)]
gdp[, year := as.integer(year)]

# isolate GDPs with a "k", delete "k", multiply by 1000
gdp_sub1 <- gdp[grep("k", per_capita_gdp)]
gdp_sub1[, per_capita_gdp := unlist(strsplit(per_capita_gdp, "k"))]
gdp_sub1[, per_capita_gdp := 1000 * as.double(per_capita_gdp)]

# GDPs no "k"
gdp_sub2 <- gdp[!grep("k", per_capita_gdp)]
gdp_sub2[, per_capita_gdp := as.double(per_capita_gdp)]

# recombine subsets
gdp <- rbindlist(list(gdp_sub1, gdp_sub2))
gdp <- gdp[order(country)]

# merge three data sets
dt <- merge(life_exp, gdp, by = c("country", "year"), all.x = FALSE)
dt <- merge(dt, regions, by = c("country"), all.x = FALSE)

# recoding
dt[eight_regions == "america_south", eight_regions := "South America"]
dt[eight_regions == "america_north", eight_regions := "North/Central America"]
dt[eight_regions == "east_asia_pacific", eight_regions := "Pacific/East Asia"]
dt[eight_regions == "europe_west", eight_regions := "Western Europe"]
dt[eight_regions == "europe_east", eight_regions := "Eastern Europe"]
dt[eight_regions == "africa_sub_saharan", eight_regions := "Sub-saharan Africa"]
dt[eight_regions == "asia_west", eight_regions := "Western Asia"]
dt[eight_regions == "africa_north", eight_regions := "Northern Africa"]
```

.pull-left[
```{r echo=FALSE, fig.width=7, fig.asp=1/1.3}
dt1 <- copy(dt)
dt1 <- dt1[year == max(year)]

ggplot(dt1, aes(x = per_capita_gdp/1000, y = lifeExp)) +
  geom_point(size = 3, alpha = 0.5) + 
  labs(x = "2021 GDP per capita (thousands Intl dollars)", 
       y = "Life expectancy in 2021 (years)", 
       title = "Each point is a country") + 
  scale_x_continuous(limits = c(0, 150)) +
  scale_y_continuous(breaks = seq(60, 80, 10)) +
  theme_graphclass(font_size = 20)
```
]
.pull-right[

<br>

```{r echo=FALSE}
x <- build_frame(
   "variable"        , "structure" |
   "life expectancy" ,"quantitative variable" |
   "GDP per capita"  , "quantitative variable" )
my_table(x)
```

<br>

<br>

<br>

"International dollar" is a hypothetical currency with the same *purchasing power parity* (PPP) as constant US dollars (here, the basis is 2011).
]


<div class="my-footer">
<span>Data source:  
<a href="https://www.gapminder.org/data/">Gapminder Foundation</a></span>
</div> 





---
class: left

#  Scatterplot, superposed

Adding a categorical variable ("Global region") to compare data subsets.

```{r}
dt1[four_regions == "europe"   , four_regions := "Europe"]
dt1[four_regions == "asia"     , four_regions := "Asia"]
dt1[four_regions == "americas" , four_regions := "Americas"]
dt1[four_regions == "africa"   , four_regions := "Africa"]
```

.pull-left[
```{r echo=FALSE, fig.width=7, fig.asp=1/1.3}
ggplot(dt1, 
       aes(x = per_capita_gdp/1000, 
           y = lifeExp, 
           color = four_regions)) +
  geom_point(size = 3, 
             shape = 16, 
             alpha = 0.9) + 
  labs(x = "2021 GDP per capita (thousands Intl dollars)", 
       y = "Life expectancy in 2021 (years)", 
       title = "Each point is a country") + 
  scale_x_continuous(limits = c(0, 150)) +
  scale_y_continuous(breaks = seq(60, 80, 10)) +
  theme_graphclass(font_size = 20) +
  theme(legend.position = c(0.8, 0.2), 
        legend.title = element_blank()) +
  scale_color_brewer(
    palette = "PRGn",
    direction = 1
  ) +
  guides(color = guide_legend(reverse = TRUE))
```
]
.pull-right[

<br>

```{r echo=FALSE}
x <- build_frame(
   "variable"        , "structure" |
   "life expectancy" ,"quantitative variable" |
   "GDP per capita"  , "quantitative variable" |
   "global region"   , "categorical variable, 4 levels")
my_table(x)
```

<br>

<br>

<br>

Design 

- Works best when clusters of subsets are distinct.

- Requires a legend if data cannot be directly labeled. 

]







---
class: left

#  Scatterplot, faceted

Same data with subsets separated into separate facets (panels).    
Facets are ordered by median life expectancy in "graph order."

```{r echo=FALSE, fig.width=14, fig.asp=0.4}
ggplot(dt1, aes(x = per_capita_gdp/1000, y = lifeExp)) +
  geom_point(size = 3, alpha = 0.5) + 
  labs(x = "2021 GDP per capita (thousands Intl dollars)", 
       y = "Life expectancy in 2021 (years)") + 
  facet_wrap(vars(reorder(eight_regions, lifeExp, median)), 
             ncol = 4, 
             as.table = FALSE) +
  scale_x_continuous(limits = c(0, 150)) +
  scale_y_continuous(breaks = seq(60, 80, 10)) +
  theme_graphclass(font_size = 18)
```

<div class="my-footer">
<span>Data source:  
<a href="https://www.gapminder.org/data/">Gapminder Foundation</a></span>
</div> 













---
class: left

# Time series

Similar to a scatterplot with time as the independent variable.    
Discrete time (e.g., months or years) is considered a categorical, not a quantitative, variable.   

```{r}
dt2 <- copy(dt)
dt2 <- dt2[, .(year, lifeExp)]
dt2[, med_lifeExp := median(lifeExp, na.rm = TRUE), by = c("year")]
dt2[, lifeExp := NULL]
dt2 <- unique(dt2)

dt2 <- copy(dt)
dt2 <- dt2[country == "United States"]
```

.pull-left[
```{r echo=FALSE, fig.width=7, fig.asp=1/1.3}
ggplot(dt2, aes(x = year, y = lifeExp)) +
  geom_line(linetype = 2) + 
  geom_point(size = 2) +
  labs(x = "Year", 
       y = "Life expectancy (years)") +
    theme_graphclass(font_size = 20) +
  scale_y_continuous(breaks = seq(50, 90, 10), limits = c(47, 83)) +
  annotate("text", 
           x = 1983, 
           y = c(73), 
           label = c("US"), 
           size = 6, 
           hjust = 0
  )
```
]

.pull-right[
```{r echo=FALSE}
x <- build_frame(
   "variable"        , "structure" |
   "life expectancy" , "quantitative variable" |
   "year"            , "categorical variable, ordinal" )
my_table(x)
```

<br>

<br>

Design 

- Dots connected by a dashed line (preferred)  

- If necessary, omit dots and use solid line
]
<div class="my-footer">
<span>Data source:  
<a href="https://www.gapminder.org/data/">Gapminder Foundation</a></span>
</div> 










---
class: left

# Time series, superposed

Time series conditioned by a categorical variable, with all lines in the same panel. 

```{r}
dt2 <- copy(dt)
dt2 <- dt2[, .(year, lifeExp)]
dt2[, med_lifeExp := median(lifeExp, na.rm = TRUE), by = c("year")]
dt2[, lifeExp := NULL]
dt2 <- unique(dt2)

dt2 <- copy(dt)
dt2 <- dt2[country %chin% c("United States", "Canada", "Peru")]
```

.pull-left[
```{r echo=FALSE, fig.width=7, fig.asp=1/1.3}
ggplot(dt2, aes(x = year, y = lifeExp, color = country)) +
  geom_line(linetype = 1, size = 1.5) + 
  labs(x = "Year", 
       y = "Life expectancy (years)") +
  theme_graphclass(font_size = 20) +
  scale_y_continuous(breaks = seq(50, 90, 10), limits = c(47, 83)) +
  annotate("text", 
           x = 1983, 
           y = c(64, 73, 80), 
           label = c("Peru", "US", "Canada"), 
           size = 6, 
           hjust = 0
  ) +
  theme(legend.position = "none") +
  scale_color_manual(values = c(rcb("dark_BG"), rcb("light_BG"), rcb("mid_BG")))
```
]

.pull-right[
```{r echo=FALSE}
x <- build_frame(
  "variable"          , "structure" |
    "life expectancy" , "quantitative variable" |
    "year"            , "categorical variable, ordinal" |
    "country"         , "categorical variable, 3 levels")
my_table(x)
```

<br>

<br>

<br>

Design 

- Use of color helps distinguish between lines that cross.  

- Labels eliminate the need for a legend. 

- Works best when lines are easily differentiated.
 
]

<div class="my-footer">
<span>Data source:  
<a href="https://www.gapminder.org/data/">Gapminder Foundation</a></span>
</div> 












---
class: left

#  Time series, faceted

  
Countries with the highest 2021 life expectancies in their region.    
Same data structure as the superposed chart.  


```{r}
dt3 <- copy(dt)
dt3 <- na.omit(dt3)
dt3 <- dt3[year == max(year)]
dt3 <- dt3[, max_lifeExp := max(lifeExp), by = "eight_regions"]
dt3 <- dt3[, .(country, lifeExp, max_lifeExp, eight_regions)]
dt3 <- dt3[lifeExp == max_lifeExp]
dt3 <- unique(dt3)
select_country <- dt3$country

dt4 <- copy(dt)
dt4 <- dt4[, .(country, year, lifeExp, eight_regions)]
dt4 <- dt4[country %chin% select_country] 
dt4[, country := factor(country, levels = c("Mauritius", "Israel", "Tunisia", "Finland", "Peru", "Canada", "Singapore", "Iceland"))]
```

```{r echo=FALSE, fig.width=14, fig.asp=0.4}
ggplot(dt4, aes(x = year, y = lifeExp)) +
  geom_line(size = 1.5) + 
  labs(x = "Year", 
       y = "Life expectancy (years)") + 
  facet_wrap(vars(country), 
             ncol = 4, 
             as.table = FALSE) +
  scale_y_continuous(breaks = seq(55, 95, 10), limits = c(53, 87)) +
  scale_x_continuous(breaks = seq(1975, 2065, 15), limits = c(1970, 2025)) +
  theme_graphclass(font_size = 18) +
  geom_text(aes(x = 1970, y = 86.5, label = eight_regions), 
            hjust = 0.05, 
            size = 5, 
            color = rcb("mid_Gray"))
```

<div class="my-footer">
<span>Data source:  
<a href="https://www.gapminder.org/data/">Gapminder Foundation</a></span>
</div> 










---
class:left

# Time series, cyclic

```{r}
dt <- fread("data/ice_extent_NH.csv", header = TRUE)
dt <- dt[, 1:13]
setnames(dt, "V1", "year")
dt <- melt(dt, 
           id.vars = "year", 
           variable.name = "month", 
           value.name = "extent")
dt <- dt[year != 1978]
dt[, hemis := "Arctic"]
dt <- unique(dt)
dt <- dt[, month := factor(month, levels = c("September", 
                                             "October", 
                                             "November", 
                                             "December", 
                                             "January", 
                                             "February", 
                                             "March", 
                                             "April", 
                                             "May", 
                                             "June", 
                                             "July", 
                                             "August"))]
dt <- dt[order(month, year)]
```

```{r echo=FALSE, fig.width=14, fig.asp=0.32}
ggplot(dt, aes(x = year, y = extent)) +
  geom_line(size = 1, na.rm = TRUE, color = rcb("dark_BG")) +
  facet_wrap(vars(month), ncol = 12, strip.position = "bottom") +
  theme_minimal() +
  labs(x = "", 
       y = "", 
       title= "Extent of arctic ice (millions sq. km.) for a given month, 1979-2021") +
  theme(axis.text.x = element_blank(), 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x = element_blank(), 
        strip.text = element_text(size = 14), 
        axis.text = element_text(size = 18), 
        plot.title = element_text(size = 18)
        ) +
  scale_y_continuous(limits = c(0, 20), breaks = seq(0, 20, 5))
```

.left-column[
A time series showing the behavior of cyclic sub-series.
]
.right-column[
```{r echo=FALSE}
x <- build_frame(
   "variable"   , "structure" |
   "ice extent" , "quantitative variable" | 
   "year"       , "categorical variable, ordinal, 43 levels" |
   "month"      , "categorical variable, ordinal, 12 levels" )
my_table(x)
```
]

<div class="my-footer">
<span>Data source: NASA National Snow and Ice Data Center  
<a href="https://nsidc.org/arcticseaicenews/sea-ice-tools/">Sea ice extent and area organized by year</a></span>
</div> 








---
class:left

# Time series, cyclic, superposed

```{r}
SH <- fread("data/ice_extent_SH.csv", header = TRUE)
SH <- SH[, 1:13]
setnames(SH, "V1", "year")
SH <- melt(SH, 
           id.vars = "year", 
           variable.name = "month", 
           value.name = "extent")
SH <- SH[year != 1978]
SH[, hemis := "Antarctic"]
SH <- unique(SH)
SH <- SH[, month := factor(month, levels = c("September", 
                                             "October", 
                                             "November", 
                                             "December", 
                                             "January", 
                                             "February", 
                                             "March", 
                                             "April", 
                                             "May", 
                                             "June", 
                                             "July", 
                                             "August"))]
SH <- SH[order(month, year)]

dt <- rbindlist(list(dt, SH))

# label data in one panel only
my_text <- dt[month == "September" & year == "1979"]

```

```{r echo=FALSE, fig.width=14, fig.asp=0.32}
ggplot(dt, aes(x = year, y = extent, color = hemis)) +
  geom_line(size = 1, na.rm = TRUE) +
  facet_wrap(vars(month), ncol = 12, strip.position = "bottom") +
  theme_minimal() +
  labs(x = "", 
       y = "", 
       title= "Extent of polar ice (millions sq. km.) for a given month, 1979-2021") +
  theme(axis.text.x = element_blank(), 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x = element_blank(), 
        strip.text = element_text(size = 14), 
        axis.text = element_text(size = 18), 
        plot.title = element_text(size = 18), 
        legend.position = "none"
        ) +
  scale_color_manual(values = c(rcb("mid_Br"), rcb("dark_BG"))) +
  geom_text(data = my_text,
            mapping = aes(x = year, 
                          y = extent + c(2, -1.7), 
                          label = hemis),
            hjust = c(0, 0),
            size = 6,
            color = rcb("mid_Gray")) +
  scale_y_continuous(limits = c(0, 20), breaks = seq(0, 20, 5))
```
.left-column[
Adding *hemisphere* as a categorical variable. 
]
.right-column[
```{r echo=FALSE}
x <- build_frame(
   "variable"   , "structure" |
   "ice extent" , "quantitative variable" | 
   "year"       , "categorical variable, ordinal, 43 levels" |
   "month"      , "categorical variable, ordinal, 12 levels" |
   "hemisphere" , "categorical variable, nominal, 2 levels")
my_table(x)
```
]

<div class="my-footer">
<span>Data source: NASA National Snow and Ice Data Center  
<a href="https://nsidc.org/arcticseaicenews/sea-ice-tools/">Sea ice extent and area organized by year</a></span>
</div> 












---
class: left

# Diverging stacked bar chart

Designed for reporting survey data.    
The quantitative variable is the percent choosing a particular response. 


<div class="my-footer">
<span>Data source: Source  
<a href="https://site">Link</a></span>
</div> 






---
class: left

# Scatterplot matrix

Designed to display the pair-wise dependence of three or more quantitative variables.

<div class="my-footer">
<span>Data source: Source  
<a href="https://site">Link</a></span>
</div> 






















---
class: left

# Conditioning chart

Designed to display the mutual dependence of three or four quantitative variables.

<div class="my-footer">
<span>Data source: Source  
<a href="https://site">Link</a></span>
</div> 





